{mscstexta4r}

### 2016-06-20 README.Rmd
Replace characters with accents in sample inputs

```{r}
docsText = c(
  "The Louvre or the Louvre Museum is the world's largest museum.",
  "Le musée du Louvre est un musée d'art et d'antiquités situé au centre de Paris.",
  "El Museo del Louvre es el museo nacional de Francia.",
  "Il Museo del Louvre a Parigi, in Francia, è uno dei più celebri musei del mondo.",
  "Der Louvre ist ein Museum in Paris."
)

@@

All Microsoft Cognitive Services components are Copyright © Microsoft.

>>>>

```{r}
docsText = c(
  "The Louvre or the Louvre Museum is the world's largest museum.",
  "Le musee du Louvre est un musee d'art et d'antiquites situe au centre de Paris.",
  "El Museo del Louvre es el museo nacional de Francia.",
  "Il Museo del Louvre a Parigi, in Francia, e uno dei piu celebri musei del mondo.",
  "Der Louvre ist ein Museum in Paris."
)

@@

All Microsoft Cognitive Services components are Copyright (c) Microsoft.
